---
title: "#WhatIEatinaDay Social Media Content and Orthorexic Tendency"
author: >
  Songyi Ahn
  <br><small style="color:black;">School of Journalism and Communication, University of Oregon</small>
date: "2026-03-??"
output: 
  html_document:
      theme: paper
      toc_float: true
      toc_collapsed: false
      toc: true
      toc_depth: 3
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(rio)
library(here)
library(tidyverse)
```

## Background

what i eat in a day, orthorexia background 

### Project Objectives

1. examine 
2. identify 

### About Data 

the data is based on something something 

## Orthorexic Tendency

Orthoresic tendency is something something and it is related to something something

### WIEIAD Message Types

messages types are 1.2.3.4.

plots

### Thin-ideal Internalization

thin-ideal internalization is how much you want

plots

### Social Appearance Comparison

social appearance comparison is tendency to compare yourself with others

plots

### Body Dissatisfaction

body dissatisfaction is the extent of 

plots

### Self-Esteem

self-esteem is how much you respect yourself and love yourself

plots

### Excessive Exercise 

excessive exercise is fixated exercising 

plots

## Predicting Orthorexic Tendency

I performed this this that that 

### Model Specification

linear regression with lasso and ridge 

### Prediction

slider style: thin-ideal internalization, social appearance comparison, body dissatisfaction, self-esteem, excessive exercise / click style: wieiad message type, eating disorder treatment experience

## Common Themes in Weight-Inclusive Responses

The data includes open-ended response from people who watched weight-inclusve videos and was instructed to write their personal opinion about nonrestictive and weight-inclsuve eating habits for your overall health and well-being.

### Word Cloud 

the word cloud shows that something something 

## Conlcusion

In conclusion, I found that 

## Reference




